%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

% \begin{tabularx}{\linewidth}{@{} C @{}}
% \Huge{Your Name} \\[7.5pt]
% \href{https://github.com/username}{\raisebox{-0.05\height}\faGithub\ username} \ $|$ \ 
% \href{https://linkedin.com/in/username}{\raisebox{-0.05\height}\faLinkedin\ username} \ $|$ \ 
% \href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
% \href{mailto:email@mysite.com}{\raisebox{-0.05\height}\faEnvelope \ email@mysite.com} \ $|$ \ 
% \href{tel:+000000000000}{\raisebox{-0.05\height}\faMobile \ +00.00.000.000} \\
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Jainam Dhruva} \\[7.5pt] % [cite: 1]
\href{mailto:jainam.dhruva@uky.edu}{\raisebox{-0.05\height}\faEnvelope \ jainam.dhruva@uky.edu} \ $|$ \ % [cite: 2]
\href{tel:+18594200596}{\raisebox{-0.05\height}\faMobile \ 859-420-0596} \ $|$ \ % [cite: 2]
Lexington, KY % [cite: 2]
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
Aug 2023 - Present & PhD in Computer Science at \textbf{University of Kentucky} \\ % [cite: 4, 5, 14]
May 2023 & B.S in Computer Science (Summa Cum Laude) at \textbf{University of Kentucky} \\ % [cite: 6, 7, 13]
May 2023 & B.S in Mathematics (Summa Cum Laude) at \textbf{University of Kentucky} \\ % [cite: 6, 8, 13]
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Research}

\begin{joblong}{Research Assistant}{Aug 2023 Present} % [cite: 10, 14]
\item Exploring machine learning ideas and optimization techniques to increase energy efficiency, reduce costs, and optimize human-feedback in Smart Grids. % [cite: 15]
\item Current projects focus on optimal control of HVAC systems and integration of EVs in Virtual Power Plants. % [cite: 16]
\item Keywords: Energy Management, Smart Grid, Machine Learning, Optimization, Internet of Things. % [cite: 17]
\end{joblong}

\begin{joblong}{Independent Study Deep Reinforcement Learning}{Jan 2023 May 2023} % [cite: 18, 20]
\item Provided a comprehensive analysis and comparison of the reinforcement learning algorithms, its computational costs, and implementation insights for DQN and PPO. % [cite: 21]
\end{joblong}

\begin{joblong}{Undergraduate Research Fellow}{May 2020 Aug 2020} % [cite: 22, 24]
\item Developed a workflow using LiDAR-based technology to capture and manipulate the the 3-D models of the crops to calculate the above-ground biomass of the crops in a field setting. % [cite: 25]
\item Implemented a new mesh algorithm for accurately capturing the biomass in lab setting. % [cite: 26]
\end{joblong}
  
\begin{joblong}{Research Assistant}{Jan 2020 May 2020} % [cite: 27, 29]
\item Assisted in a project that aimed at quantifying the influence of various directors and officers at different companies by analyzing their previous experiences. % [cite: 30]
\item Primary duties included collection and verification of the data for the project, and exploring python scripts for automation. % [cite: 31]
\end{joblong}


\section{Teaching}

\begin{joblong}{Computer Science Teaching Assistant}{Aug 2023 May 2024} % [cite: 33, 35]
\item Facilitated learning in Systems Programming (CS 270) by guiding students through key topics in computer architecture, operating systems, and networks from a programmer's perspective. % [cite: 36]
\item Managed homework, project, and lab grading for 60 students, ensuring timely feedback and academic growth. % [cite: 37]
\end{joblong}

\begin{joblong}{Computer Science Grader}{Jan 2023 May 2023} % [cite: 38, 40]
\item Led grading for CS 270, providing assessments for 140 students to help them achieve foundational programming skills essential for future coursework. % [cite: 41]
\end{joblong}

\begin{joblong}{Mathematics Undergraduate Assistant}{Jan 2023 May 2023} % [cite: 42, 44]
\item Tutored students in Introductory Calculus, Multivariate Calculus, and Differential Equations, developing both their problem-solving abilities and confidence in advanced math topics. % [cite: 45]
\end{joblong}

\begin{joblong}{Computer Science Tutor}{Jan 2022 Jan 2023} % [cite: 46, 48]
\item Supported student learning across core computer science subjects, including data structures, algorithms, and computer systems, equipping them with essential analytical skills. % [cite: 49]
\end{joblong}


\section{Internships}

\begin{joblong}{Software Engineer Intern}{May 2022 Dec 2022} % [cite: 55, 57]
\item Developed and maintained mobile first, responsive, secure, and WCAG compliant sites utilizing a content management system for over 200 financial institutions. % [cite: 58]
\item Participated in code reviews, providing constructive feedback and actively collaborating with team members to improve code quality and maintain best practices. % [cite: 59]
\item Collaborated with cross-functional teams, clients, and third-party vendors to develop and integrate front facing features and custom work items, generating over \$30,000 in profit. % [cite: 60]
\end{joblong}

\begin{joblong}{Software Engineer Intern}{May 2021 Aug 2021} % [cite: 61, 63]
\item Developed a faster, efficient, and automated tool to extract colored linear features from Point Clouds. % [cite: 64]
\item Updated deprecated modules in open source libraries written in C++ and CUDA for simplified integration. % [cite: 65]
\item Documented the implementation of the tool, the limitations, and the critical bugs encountered in the module. % [cite: 66]
\end{joblong}

\section{Awards and Honors}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item IEEE PESGM 2025 Student Support Program Poster Competition Presentation % [cite: 89]
\item UKY 3MT-3 Minute Presentation 2024 3rd Place Winner (Early researchers track) % [cite: 89]
\item UKY CS 3MT 2024 Honorable Mention % [cite: 90]
\item TPEC 2024 Travel Grant Attend Texas Energy and Power Conference 2024 % [cite: 91]
\end{itemize}

\section{Posters}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item "Multi-Objective Control for V2G-Enabled Grids: Balancing Grid Stability and Battery Degradation" (IEEE PESGM) % [cite: 93]
\item "Using Deep Reinforcement Learning to Solve OpenAI's 'Car Racing Environment" (UKY Undergraduate Research Showcase, 2023) % [cite: 93]
\end{itemize}

\section{Leadership}
\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{Treasurer} & ACM Chapter at the University of Kentucky & Aug 2023 Present \\ % 
\textbf{International Student Ambassador} & University of Kentucky & Aug 2019 May 2023 \\ % 
\textbf{Sponsorship Chair} & Cathacks, ACM Chapter & Aug 2022 May 2023 \\ % 
\textbf{Resident Advisor} & University of Kentucky & Aug 2020 May 2022 \\ % 
\end{tabularx}

\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages & \normalsize{Python, C/C++, SQL, JavaScript, HTML/CSS, PHP.} \\ % [cite: 95]
Libraries & \normalsize{PyTorch, Gurobi, Hugging Face, OpenAI Gymnasium, NumPy, Matplotlib.} \\ % [cite: 96]
Other & \normalsize{EnergyPlus, Unix, Git.} \\ % [cite: 96]
\end{tabularx}



%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{refsection}[citations.bib]
\nocite{*} % This tells LaTeX to print all entries from the .bib file
\printbibliography[heading=none]
\end{refsection}


\section{Professional Activities}

\textbf{Journal Proceedings Peer Review}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item IEEE Transactions on Network Science and Engineering (TNSE) [cite: 81]
\item Elsevier Pervasive and Mobile Computing (PMC) [cite: 82]
\item Elsevier Computer Networks [cite: 83]
\end{itemize}

\textbf{Conference Proceedings Peer Review}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item IEEE International Conference on Computer Communications (INFOCOM 2026) [cite: 85]
\item IEEE International International Conference on Distributed Computing and Networking (ICDCN 2026) [cite: 86]
\item IEEE International Conference on Pervasive Computing and Communications (PerCom 2025) [cite: 87]
\item IEEE International Conference on Distributed Computing Systems (ICDCS 2024, 2025) [cite: 88]
\item IEEE International Conference on Communication (ICC 2024, 2025) [cite: 89]
\item IEEE Intl. Conf. on Distributed Computing in Smart Systems and the Internet of Things (DCOSS-IoT 2024, 2025) [cite: 90]
\item IEEE International Conference on Smart Computing (SMARTCOMP 2025) [cite: 91]
\item IEEE International Conference on Mobile Ad-Hoc and Smart Systems (MASS 2025) [cite: 92]
\item IFIP Networking Conference (IFIP Networking 2024) [cite: 93]
\item IEEE International Symposium on a World of Wireless, Mobile and Multimedia Networks (WoWMOM 2024) [cite: 94]
\item IEEE/ACM International Symposium on Quality of Service (IWQOS 2024) [cite: 95]
\item International Conference on COMmunication Systems \& NETworkS (COMSNETS 2025) [cite: 96]
\end{itemize}

\textbf{Invited Talks and Presentations}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item CS270 Guest Lecture: Memory Hierarchy and Caching [cite: 97]
\item CatHacks X Seminar: Introduction to Git and Github [cite: 97]
\item CatHacks IX Seminar: Introduction to Git and Github [cite: 97]
\item CS 499: Senior Design Class Graduate Panel [cite: 97]
\item EGR 101 Panel: Engineering Career Panel [cite: 97]
\end{itemize}


%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Some Skills &  \normalsize{This, That, Some of this and that etc.}\\
Some More Skills  &  \normalsize{Also some more of this, Some more that, And some of this and that etc.}\\  
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
